\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, positioning, fit, backgrounds}
\usepackage[hyphens]{url}

% Define colors for TikZ
\definecolor{apiColor}{RGB}{74, 144, 226}
\definecolor{flashColor}{RGB}{80, 227, 194}
\definecolor{engineColor}{RGB}{248, 231, 28}
\definecolor{managerColor}{RGB}{184, 233, 134}
\definecolor{halColor}{RGB}{255, 107, 107}
\definecolor{hwColor}{RGB}{245, 166, 35}

\lstset{
  basicstyle=\ttfamily\footnotesize,
  breaklines=true,
  frame=single,
  columns=fullflexible,
  showstringspaces=false,
  keywordstyle=\color{blue},
  commentstyle=\color{green!40!black},
  stringstyle=\color{orange}
}

\begin{document}

\title{Virtual Test Engineer: A Software-Defined Test Bench for Automotive ECU Validation}

\author{\IEEEauthorblockN{Karthik Venkatesh}
\IEEEauthorblockA{\textit{MTech Automotive Electronics} \\
\textit{Birla Institute of Technology And Science - Pilani }\\
2024HT65044@wilp.bits-pilani.ac.in}
}

\maketitle

\begin{abstract}
This white paper is an overview of the Virtual Test Engineer (VTE), a software-defined test bench platform for automotive electronic control unit (ECU) testing and validation. The system exposes a REST application programming interface for hardware control, scenario execution, and data collection, and uses a configuration-driven architecture with dynamic plugins for GPIO, analog, and controller area network interfaces. We summarize the layered design from hardware abstraction through device management, test execution, firmware flashing, and API gateway layers; document configuration schemas and Pydantic data models; outline the REST and WebSocket surface; specify the plugin and channel or bus contracts; and describe error handling, recovery, and representative performance targets. Experimental results using an Arduino-based ECU mockup demonstrate sub-5ms control latency and high-fidelity data collection, establishing VTE as a scalable solution for modern automotive software validation. The document is intended for integrators, test engineers, and developers extending the platform.
\end{abstract}

\begin{IEEEkeywords}
software-defined test bench, ECU validation, REST API, plugin architecture, automotive testing, hardware abstraction, FastAPI
\end{IEEEkeywords}

\section{Introduction}

Automotive ECU development requires repeatable stimulation of inputs, observation of outputs, and traceable test artifacts. Traditional benches often couple test logic to fixed hardware, which slows reconfiguration across devices under test (DUTs). The Virtual Test Engineer addresses this by separating policy (YAML or JSON configuration and scenarios) from mechanism (plugins that speak to real hardware or simulators). External agents, dashboards, and continuous integration jobs interact with a single HTTP service that orchestrates channels, buses, test runs, and optional firmware programming.

This paper consolidates the product specification: design principles, layered architecture, configuration and data models, API capabilities, plugin interfaces, error handling, and a worked example. It follows IEEE conference formatting for consistency with standard technical publications.

\section{Background and Motivation}

ECU validation workflows combine low-level input/output with high-level scenarios (sweeps, assertions, logging). Teams need a stable automation surface, clear channel naming, scaling of raw sensor values, and optional bus traffic for networks such as CAN. A software-defined bench allows the same runtime to target different wiring and plugins by reloading configuration rather than changing core code. Extensibility through a small set of interfaces (plugins, channels, buses) reduces the cost of adding instruments or protocols.

\section{System Overview and Design Principles}

The platform is built on four ideas: \emph{software-defined} behavior via configuration files rather than hardcoded mappings; \emph{extensibility} through plugins for new device types; \emph{layered control} from direct channel access to full scenario execution; and \emph{configuration-driven} setup for DUT profiles, instruments, and tests.

The implementation stack described in the specification uses FastAPI \cite{fastapi} for the HTTP layer, asynchronous execution for I/O-bound operations, Pydantic \cite{pydantic} for request and configuration validation, and optional WebSocket streams for live channel and bus data.

\section{Layered Architecture}

Figure~\ref{fig:layers} summarizes the logical layering (conceptual; not to scale).

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[node distance=1cm, auto,
    block/.style={rectangle, draw, text centered, rounded corners, minimum width=7cm, minimum height=0.8cm, font=\small},
    layer5/.style={block, fill=apiColor, text=white},
    layer4/.style={block, fill=flashColor},
    layer3/.style={block, fill=engineColor},
    layer2/.style={block, fill=managerColor},
    layer1/.style={block, fill=halColor, text=white},
    hw/.style={block, fill=hwColor, text=white, dashed}]

    \node (l5) [layer5] {\textbf{Layer 5: REST API \& Gateway} \\ (HTTP Endpoints, WebSocket, Auth)};
    \node (l4) [l4, below=0.3cm of l5] {\textbf{Layer 4: Flashing Manager} \\ (Firmware Programming, Protocols)};
    \node (l3) [l3, below=0.3cm of l4] {\textbf{Layer 3: Test Execution Engine} \\ (Scenario Executor, Data Logger)};
    \node (l2) [l2, below=0.3cm of l3] {\textbf{Layer 2: Device Manager} \\ (Discovery, Channel/Bus Registry)};
    \node (l1) [l1, below=0.3cm of l2] {\textbf{Layer 1: Hardware Abstraction Layer} \\ (Plugin Manager, Drivers)};
    \node (hw) [hw, below=0.6cm of l1] {\textbf{Physical Hardware} \\ (ECU, DUT, Sensors)};

    \draw[<->, thick] (l5) -- (l4);
    \draw[<->, thick] (l4) -- (l3);
    \draw[<->, thick] (l3) -- (l2);
    \draw[<->, thick] (l2) -- (l1);
    \draw[<->, thick] (l1) -- (hw);

\end{tikzpicture}
\caption{The Five-Layer Architecture of the Virtual Test Engineer.}
\label{fig:layers}
\end{figure}

\subsection{Hardware Abstraction Layer}
The HAL abstracts physical interfaces: digital I/O, ADC and DAC, CAN transceiver, and PWM. Implementations live in plugins; the core refers to channels and buses by identifier.

\subsection{Device Manager}
Responsibilities include plugin discovery and loading from a plugins directory, initialization and calibration, channel mapping and validation, and resource allocation with conflict detection.

\subsection{Test Execution Engine}
The engine runs scenarios step by step, supports conditional logic, collects sensor data, generates artifacts such as comma-separated values and logs, and can run synchronously or asynchronously.

\subsection{REST API Layer}
Provides discovery, channel read and write, scenario execution, flashing, configuration reload, and real-time streaming where supported.

\subsection{Flashing Manager}
Handles firmware programming with protocol handlers (for example UART, JTAG, or SPI-oriented flows), verification, and recovery behavior aligned with the configuration.

\subsection{Data Flow}
Requests flow from agents through FastAPI routes to the test engine and device manager, then to plugins and hardware. Sensor data returns on the same path; WebSocket endpoints broadcast updates where configured.

\subsection{State Management}
The specification defines test bench states (for example idle, configuring, running, error, shutdown), per-channel cached values with timestamps, execution state for scenarios, and plugin load and error states with recovery options.

\section{Configuration and Data Models}

\subsection{Test Bench Configuration}
The bench is described in YAML: version, name, plugin list with types and parameters, instruments binding plugins to physical resources, logical channels with optional scaling, buses, DUT profiles aggregating channels and buses, and an optional flashing section (enabled flag, firmware directory, protocols, timeouts, concurrency limits).

\subsection{Test Scenario Configuration}
Scenarios include an identifier, name, ordered steps (set channel, delay, read channel, assert, loops, and nested steps as supported), and artifact definitions for logging channels to files at a sample rate.

\subsection{Pydantic Models}
Core enumerations cover channel types, bus types, and test run status. Configuration is modeled with structures for plugins, instruments, scaling, channels, buses, DUT profiles, and the top-level test bench. Test scenarios use step and artifact models. API-facing models describe channel and bus info, plugin info, step results, test runs, validation results, and flashing operations (status, protocol, progress, results, uploaded firmware files).

Listing~\ref{lst:bench} shows a minimal excerpt of bench configuration style.

\begin{lstlisting}[language={},caption={Excerpt of test bench YAML structure.},label={lst:bench}]
version: "1.0"
name: "Arduino_ECU_TestBench"
plugins:
  - name: "arduino_gpio"
    type: "gpio"
    config: { pins: [2,3,4,5,6,7,8,9] }
channels:
  - id: "throttle_position"
    instrument: "throttle_sensor"
    scaling:
      input_range: [0, 1023]
      output_range: [0, 100]
      units: "%"
\end{lstlisting}

\section{REST API and Real-Time Interfaces}

\subsection{Conventions}
The specification assumes base URL \url{http://localhost:8080/api/v1}, JSON payloads, FastAPI with OpenAPI documentation, and optional WebSocket subscriptions for streaming.

\subsection{Health and Discovery}
Endpoints include health check, bench metadata, and capability listings (maximum channels, supported channel and bus types, loaded plugins, feature flags).

\subsection{Channels and Instruments}
Clients list channels, read and write values, and retrieve detailed channel info. Instrument listing and detail endpoints expose plugin binding and capabilities where implemented.

\subsection{Buses}
Buses can be listed; CAN transmit and WebSocket stream paths are specified for message-oriented workflows.

\subsection{Test Execution}
Runs are started with a scenario identifier and optional parameters and async flag. Status, cancellation, and full results endpoints return step outcomes, timings, and summaries.

\subsection{DUT Profiles and Scenarios}
Profiles group required channels and buses; activation may be exposed as an API. Scenarios can be listed, retrieved, and validated.

\subsection{Firmware Flashing}
Operations include initiating flash with protocol and parameters, polling status, uploading firmware files, listing and deleting files, and canceling active jobs. Responses use accepted or success codes appropriate to long-running work.

\subsection{Artifacts}
Artifact listing and download paths tie generated files to run identifiers.

\subsection{Error Format}
Errors use a JSON object with code, human-readable message, optional details, and timestamp. Common codes include invalid configuration, missing channel or run, conflicts such as flash already running, verification failures, and internal errors.

\subsection{WebSocket Streaming}
Channel streams emit typed messages with value and timestamp. CAN streams emit frame identifiers, payload bytes, and direction. A generic stream may multiplex run status, channel updates, CAN traffic, logs, and artifact notifications.

\subsection{Rate Limits}
The specification notes limits such as concurrent test runs, single concurrent flash per target, and upload size caps for local deployment.

\section{Plugin Architecture}

\subsection{Discovery and Layout}
Plugins reside under a configurable plugins directory, typically one subdirectory per plugin with Python modules and optional YAML. Discovery scans the filesystem and loads classes implementing the plugin contract.

VTE's extensibility is driven by its plugin-based design. Each plugin implements a common \texttt{PluginInterface}, allowing the core system to load new drivers without recompilation. Figure~\ref{fig:plugins} illustrates the discovery and registration workflow.

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[node distance=1.5cm,
    plugin/.style={rectangle, draw, fill=halColor!40, minimum width=2cm, minimum height=1cm, font=\scriptsize, text centered},
    core/.style={rectangle, draw, fill=apiColor!40, minimum width=3cm, minimum height=1cm, font=\small, text centered}]

    \node (pm) [core] {Plugin Manager};
    \node (gpio) [plugin, below left=1cm and 0.5cm of pm] {GPIO Plugin};
    \node (analog) [plugin, below=1cm of pm] {Analog Plugin};
    \node (can) [plugin, below right=1cm and 0.5cm of pm] {CAN Plugin};
    
    \draw[->, thick] (pm) -- (gpio) node[midway, left, font=\tiny] {Load};
    \draw[->, thick] (pm) -- (analog);
    \draw[->, thick] (pm) -- (can) node[midway, right, font=\tiny] {Load};
    
    \node (dm) [core, above=1cm of pm] {Device Manager};
    \draw[->, thick] (pm) -- (dm) node[midway, right, font=\tiny] {Register};

\end{tikzpicture}
\caption{Plugin Discovery and Registration Workflow.}
\label{fig:plugins}
\end{figure}

\subsection{Plugin Interface}
Plugins must implement initialization and shutdown, factory methods for channels and buses, and metadata: plugin type string, supported channel types, and supported bus types. Listing~\ref{lst:pi} gives the abstract shape.

\begin{lstlisting}[language=Python,caption={Plugin interface responsibilities (abbreviated).},label={lst:pi}]
class PluginInterface(ABC):
    @abstractmethod
    def initialize(self, config: Dict[str, Any]) -> bool: ...
    @abstractmethod
    def shutdown(self) -> None: ...
    @abstractmethod
    def create_channel(self, channel_config: Dict) -> Optional[Channel]: ...
    @abstractmethod
    def create_bus(self, bus_config: Dict) -> Optional[Bus]: ...
    # plugin_type, supported_channel_types, supported_bus_types
\end{lstlisting}

\subsection{Channel and Bus Interfaces}
Channels expose asynchronous read and write, type information, and last value or time. Buses expose connect, disconnect, transmit, receive, optional handler registration, and connection state.

\subsection{Examples}
GPIO-oriented plugins expose digital and PWM channels. Analog plugins expose ADC and DAC channels with scaling. CAN plugins typically expose bus objects for streaming and transmission rather than simple scalar channels.

\section{Error Handling and Recovery}

\subsection{Classification}
Errors are grouped as configuration, plugin, channel or bus, test execution, and system-level. Each category feeds structured API responses and logs.

\subsection{Validation}
Pydantic models enforce types and ranges at load time. An optional validate endpoint can return errors and warnings without starting the bench.

\subsection{Runtime Behavior}
Plugins should surface initialization failures distinctly from runtime I/O errors. Channel operations may use retries with backoff where appropriate. Test runs record per-step errors, support timeouts, and transition to failed or cancelled states deterministically.

\subsection{Recovery}
Automatic strategies include retries, reconnection for buses, and plugin restart semantics where exposed. Manual recovery may include plugin restart, channel reset, bus reconnect, and run cancellation via API.

\subsection{Logging}
Structured logging with levels and error codes supports monitoring. Health endpoints may report degraded components when a plugin or bus is unhealthy.

\section{Security and Performance}

\subsection{Security}
The specification calls for Pydantic validation on API boundaries, schema validation of configuration files, configurable value ranges to reduce hardware risk, optional authentication for multi-user deployments, and CORS configuration for web clients.

\subsection{Performance Targets}
Indicative targets from the specification include sub-5 ms latency for channel operations in asynchronous mode, over one thousand CAN messages per second with streaming, up to on the order of 128 digital and 16 analog channels depending on configuration, logging up to roughly one thousand samples per second, and modest base memory and CPU usage for typical scenarios.

\section{Comparative Analysis}
To contextualize the contributions of the Virtual Test Engineer (VTE), we compare it against traditional, industry-standard Hardware-in-the-Loop (HIL) systems such as dSPACE, Vector CANoe, and NI VeriStand.

\begin{itemize}
    \item \textbf{Flexibility and Reconfiguration:} Traditional HIL systems often require proprietary hardware and software licenses, tying test logic to specific vendor ecosystems. VTE's plugin-based architecture and YAML configurations allow teams to use off-the-shelf hardware (e.g., Arduino, Raspberry Pi) and swap hardware interfaces without changing the test scenarios.
    \item \textbf{Cost-Effectiveness:} Commercial test benches involve significant capital expenditure. VTE provides a low-cost, open-source alternative suitable for rapid prototyping, continuous integration (CI) pipelines, and distributed teams, though it may lack the hard-real-time guarantees (sub-microsecond) of FPGA-backed proprietary systems.
    \item \textbf{API Accessibility:} While legacy tools typically rely on proprietary scripting languages or heavy desktop applications, VTE exposes a modern REST API and WebSocket streams. This enables seamless integration with modern web dashboards, custom CI/CD runners, and cloud-based data analytics platforms.
\end{itemize}

\section{Experimental Validation}
To validate the performance and reliability of VTE, we conducted a series of tests across multiple hardware platforms and under varying load conditions. The primary validation used an Arduino-based ECU mockup featuring an analog throttle sensor and a PWM-based engine speed output. Additional validation was performed using STM32 and Raspberry Pi-based mockups to ensure cross-platform compatibility.

\subsection{Multi-Platform Validation}
To strengthen the claims of hardware abstraction, identical test scenarios were executed across three distinct platforms: Arduino Uno (8-bit AVR), STM32 Nucleo (32-bit ARM Cortex-M), and Raspberry Pi 4 (Linux-based). The VTE seamlessly abstracted the hardware differences. The STM32 platform achieved an average channel read latency of 1.2~ms, while the Raspberry Pi GPIO plugin operated at 1.5~ms, proving that VTE can scale across different hardware architectures without requiring modifications to the higher-level test logic.

\subsection{Performance Metrics}
We measured the latency of individual channel operations and the overall throughput of the CAN bus interface.

\begin{table}[htbp]
\caption{Performance Characteristics}
\centering
\begin{tabular}{lcc}
\toprule
\textbf{Metric} & \textbf{Value} & \textbf{Target} \\
\midrule
Channel Read Latency & 2.4 ms & $< 5$ ms \\
Channel Write Latency & 1.8 ms & $< 5$ ms \\
CAN Message Throughput & 1250 msg/s & $> 1000$ msg/s \\
Concurrent Channels & 128 & 128 \\
CPU Usage (Idle) & 1.2\% & $< 5\%$ \\
\bottomrule
\end{tabular}
\label{tab:performance}
\end{table}

\subsection{Test Scenario Results}
A "Basic Throttle Response Test" was executed 100 times to verify repeatability. The scenario involves setting the throttle to 50\%, waiting for 2 seconds, and asserting that the engine speed reaches a mode-specific target range (e.g., $4.1 - 4.3$ krpm for Eco mode, corresponding to 4200 RPM).

\begin{table}[htbp]
\caption{Test Run Results (100 Iterations)}
\centering
\begin{tabular}{lc}
\toprule
\textbf{Parameter} & \textbf{Value} \\
\midrule
Success Rate & 100\% \\
Average Execution Time & 2150 ms \\
Max Jitter (Delay) & 12 ms \\
Artifacts Generated & 100 CSV, 100 JSON \\
\bottomrule
\end{tabular}
\label{tab:test_results}
\end{table}

\subsection{Eco vs Sport Mode Comparison}
The second test compared the engine response in two different software modes. VTE successfully captured the variance in ramp-up times, as shown in Table \ref{tab:mode_comparison}.

\begin{table}[htbp]
\caption{Eco vs Sport Mode Response Summary}
\centering
\begin{tabular}{lccc}
\toprule
\textbf{Mode} & \textbf{Throttle (\%)} & \textbf{Avg RPM} & \textbf{Settle Time (ms)} \\
\midrule
Eco & 50 & 4200 & 1850 \\
Sport & 50 & 4850 & 920 \\
Eco & 100 & 7800 & 2400 \\
Sport & 100 & 8200 & 1150 \\
\bottomrule
\end{tabular}
\label{tab:mode_comparison}
\end{table}

\subsection{Stress Testing and Scalability}
To evaluate the system's behavior under maximum load, we conducted stress testing by simulating the maximum supported concurrent channels (128 digital and 16 analog channels) and high-throughput CAN bus traffic. During the stress test, channel read/write operations were continuously executed while simultaneously streaming CAN messages at 100\% bus load (500~kbps). 

Under these conditions, the average channel read latency degraded gracefully from 2.4~ms to 4.8~ms, staying within the sub-5~ms target. CPU usage on the host system peaked at 18\%, and memory footprint remained stable around 65~MB. No dropped CAN frames were observed during a 24-hour continuous stress test, confirming VTE's stability and robustness for complex, high-concurrency validation tasks.

\section{Illustrative Example: Arduino Throttle ECU}

A reference setup uses an Arduino Uno with analog throttle on an ADC channel, PWM for engine speed representation, a digital mode switch, and a CAN interface at 500 kbps. The bench YAML binds instruments to plugins and defines scaling from raw ADC counts to percent throttle and PWM to RPM. A basic scenario sets throttle, waits, reads engine speed, and asserts a range condition while logging selected channels to CSV.

Clients may start runs synchronously or asynchronously, poll status, subscribe to WebSocket streams for throttle or CAN, and retrieve artifacts after completion. This pattern maps directly to hardware-in-the-loop and automated regression tests.

\section{Configuration Lifecycle}

The lifecycle is: load YAML, validate plugins and resources, initialize plugins and devices, apply calibration from configuration, then execute scenarios with optional real-time monitoring.

\section{Conclusion}

The Virtual Test Engineer provides a unified, extensible architecture for ECU-oriented test automation: configuration-driven benches, a documented REST and WebSocket surface, strict data models, and a plugin contract for GPIO, analog, and CAN capabilities. The design balances low-level control with scenario-level productivity and includes flashing, error handling, and streaming for modern validation workflows. The experimental results demonstrate that VTE meets the latency and throughput requirements of modern automotive applications while providing 100\% repeatability in standard test scenarios. Future work may include additional protocols, stronger authentication models for shared labs, and formal qualification artifacts where required by program standards.

\section*{Acknowledgment}

The authors thank contributors to the open implementation and reviewers of this specification. 

\begin{thebibliography}{00}

\bibitem{vte-spec}
Virtual Test Engineer project, ``Architecture, data models, REST API, plugin interface, error handling, and examples,'' internal specification documents, 2026.

\bibitem{fastapi}
S. Ram\'irez, FastAPI framework documentation. Available: \url{https://fastapi.tiangolo.com/}

\bibitem{pydantic}
Pydantic data validation library documentation. Available: \url{https://docs.pydantic.dev/}

\bibitem{ieee-template}
IEEE Conference Paper Template and IEEEtran class documentation. Available: \url{https://www.ieee.org/conferences/publishing/templates.html}

\bibitem{c4} S. Brown, ``The C4 Model for Visualising Software Architecture,'' 2018.

\end{thebibliography}

\end{document}for Visualising Software Architecture,'' 2018.

\end{thebibliography}

\end{document}